---
title: "Length of stay: Univariate"
output:
  html_document: default
  pdf_document: default
date: "2023-06-02"
---

v1

1. Dataset: aou_los_v1.RData
2. EDA for los
3. Univariate for los

v2

1. Dataset: aou_los_v2.RData

v3

1. Dataset: aou_los_v3.RData
2. Additional comorbidities
3. Migrated from splines to splines2 
(Periodic B-splines and Rcpp Armadillo performance boost) https://cran.r-project.org/web/packages/splines2/vignettes/splines2-intro.html#b-spline-basis-functions

v4

1. Dataset: aou_los_v6.RData

v5

1. Dataset: aou_los_v7.RData

v6 
1. Site adjustment

v7
1. Dataset: aou_los_v8.RData (insurance)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning = F,results = T)
rm(list = ls())
library(ggstatsplot)
library(cowplot)
library(tidyverse)
library(foreign)
library(patchwork)
library(tableone)
library(MASS)
library(lubridate)
library(lme4)
library(splines2)
library(rstanarm)
cbPalette <- c("#E64B35", "#4DBBD5")
load("data/aou_los_v8.RData")
source("helpers.R")
 # load("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


 
```{r}
levels(data$concept_name_visit)

data<-data %>%
  mutate(prolongedStay=factor(if_else(los<2,"No","Yes"),
                      levels =c("No","Yes") ))
data$readmission10dNum<-as.numeric(data$readmission10d)-1
data$readmission30dNum<-as.numeric(data$readmission30d)-1
summary(data)

data$ehrsite=as.numeric(factor(data$src_id))
data$s.age<-c(scale(data$ageatvisit,center = T))
data$s.dep<-c(scale(data$dep_idx,center = T))

```


```{r}
hist(data$dep_idx,32)
hist(scale(data$dep_idx),32)
hist(scale(data$dep_idx,center = T),32)
hist(scale(data$dep_idx,center = T,scale = F),32)
```


# Individual 

```{r}

stan.uni.nb.ri.age <- stan_glmer(
  los ~
    s.age:sex_at_birth +
    # race3 +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1500,QR=TRUE,
  seed = 12345
)
# summary(stan.uni.nb.ri.race)
coefs<-mcmc_post_ci(stan.uni.nb.ri.age,0.95,34)$df
coefs %>% dplyr::select(HR)

save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```





# Race

```{r}
stan.uni.nb.ri.race <- stan_glmer(
  los ~
    race3 +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 1),
  prior_intercept = normal(0, 1),
  chains=8,
  cores=8,refresh=5,
  iter=500,QR=TRUE,
  seed = 12345
)
# summary(stan.uni.nb.ri.race)
coefs<-mcmc_post_ci(stan.uni.nb.ri.race,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp2
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## hcType1

```{r}
glmer.uni.nb.ri.hctype1 <- glmer.nb(
  los ~
    hcType1+
    (1 | id)+(1|ehrsite),
  data = data,
  nAGQ = 0,
  glmerControl(
    optimizer = "bobyqa",
    calc.derivs = FALSE,
    optCtrl = list(maxfun = 2e5)
  )
)
gtsummary::tbl_regression(glmer.uni.nb.ri.hctype1,exponentiate=T)


##### Bayesian
stan.uni.nb.ri.hctype1 <- stan_glmer(
  los ~
    hcType1 +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)
# summary(stan.uni.nb.ri.race)
coefs<-mcmc_post_ci(stan.uni.nb.ri.hctype1,0.95,34)$df
coefs %>% dplyr::select(HR)
#cp3
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


```{r}
glmer.uni.nb.ri.hctype2 <- glmer.nb(
  los ~
    hcType2+
    (1 | id)+(1|ehrsite),
  data = data,
  nAGQ = 0,
  glmerControl(
    optimizer = "bobyqa",
    calc.derivs = FALSE,
    optCtrl = list(maxfun = 2e5)
  )
)
gtsummary::tbl_regression(glmer.uni.nb.ri.hctype2,exponentiate=T)

##### Bayesian
stan.uni.nb.ri.hctype2 <- stan_glmer(
  los ~
    hcType2 +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)
# summary(stan.uni.nb.ri.race)
coefs<-mcmc_post_ci(stan.uni.nb.ri.hctype2,0.95,34)$df
coefs %>% dplyr::select(HR)
#cp3
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


```{r}
glmer.uni.nb.ri.hctype3<- glmer.nb(
  los ~
    hcType1+race3+
    (1 | id)+(1|ehrsite),
  data = data,
  nAGQ = 0,
  glmerControl(
    optimizer = "bobyqa",
    calc.derivs = FALSE,
    optCtrl = list(maxfun = 2e5)
  )
)
gtsummary::tbl_regression(glmer.uni.nb.ri.hctype3,exponentiate=T)
```

```{r}
glmer.uni.nb.ri.hctype4<- glmer.nb(
  los ~
    hcType1:race3+
    (1 | id)+(1|ehrsite),
  data = data,
  nAGQ = 0,
  glmerControl(
    optimizer = "bobyqa",
    calc.derivs = FALSE,
    optCtrl = list(maxfun = 2e5)
  )
)
gtsummary::tbl_regression(glmer.uni.nb.ri.hctype4,exponentiate=T)
```


```{r}
glmer.uni.nb.ri.hctype5<- glmer.nb(
  los ~
    hcType1*race3+
    (1 | id)+(1|ehrsite),
  data = data,
  nAGQ = 0,
  glmerControl(
    optimizer = "bobyqa",
    calc.derivs = FALSE,
    optCtrl = list(maxfun = 2e5)
  )
)
gtsummary::tbl_regression(glmer.uni.nb.ri.hctype5,exponentiate=T)
```

```{r}
glmer.uni.nb.ri.hctype6<- glmer.nb(
  los ~
    hcType1*race3+s.dep+
    (1 | id)+(1|ehrsite),
  data = data,
  nAGQ = 0,
  glmerControl(
    optimizer = "bobyqa",
    calc.derivs = FALSE,
    optCtrl = list(maxfun = 2e5)
  )
)
gtsummary::tbl_regression(glmer.uni.nb.ri.hctype6,exponentiate=T)
```


## Season

```{r}

##### Bayesian
stan.uni.nb.ri.season <- stan_glmer(
  los ~
    season +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)
# summary(stan.uni.nb.ri.race)
coefs<-mcmc_post_ci(stan.uni.nb.ri.season,0.95,34)$df
coefs %>% dplyr::select(HR)
#cp3
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```

#Day of admission

```{r}
###### bayesian
stan.uni.nb.ri.doa <- stan_glmer(
  los ~
    weekend +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.doa,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp4
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


# Deprivation non normalized

```{r}
glmer.uni.nb.ri.depidx<- glmer.nb(
  los ~
    dep_idx+
    (1 | id)+(1|ehrsite),
  data = data,
  nAGQ = 0,
  glmerControl(
    optimizer = "bobyqa",
    calc.derivs = FALSE,
    optCtrl = list(maxfun = 2e5)
  )
)
gtsummary::tbl_regression(glmer.uni.nb.ri.depidx,exponentiate=T)

###### bayesian
stan.uni.nb.ri.depidx <- stan_glmer(
  los ~
    dep_idx +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 1),
  prior_intercept = normal(0, 1),
  chains=4,
  cores=8,refresh=50,
  iter=1000,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.depidx,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```

# Deprivation normalized

```{r}
glmer.uni.nb.ri.sdep<- glmer.nb(
  los ~
    s.dep+
    (1 | id)+(1|ehrsite),
  data = data,
  nAGQ = 0,
  glmerControl(
    optimizer = "bobyqa",
    calc.derivs = FALSE,
    optCtrl = list(maxfun = 2e5)
  )
)
gtsummary::tbl_regression(glmer.uni.nb.ri.sdep,exponentiate=T)

###### bayesian
stan.uni.nb.ri.sdep <- stan_glmer(
  los ~
    s.dep +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 1),
  prior_intercept = normal(0, 1),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.sdep,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```



# Comorbidities

## Atopic dermatitis

```{r}
###### bayesian
stan.uni.nb.ri.ad <- stan_glmer(
  los ~
    AD.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 1),
  prior_intercept = normal(0, 1),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.ad,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```

## Allergic rhinitis

```{r}
###### bayesian
stan.uni.nb.ri.ar <- stan_glmer(
  los ~
    AR.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.ar,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## Cancer

```{r}
###### bayesian
stan.uni.nb.ri.cancer <- stan_glmer(
  los ~
    Cancer.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.cancer,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## CHD

```{r}
###### bayesian
stan.uni.nb.ri.chd <- stan_glmer(
  los ~
    CHD.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.chd,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```

## CKD

```{r}
###### bayesian
stan.uni.nb.ri.ckd <- stan_glmer(
  los ~
    CKD.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.ckd,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


### COPD

```{r}
###### bayesian
stan.uni.nb.ri.copd <- stan_glmer(
  los ~
    COPD.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.copd,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## Depression

```{r}
###### bayesian
stan.uni.nb.ri.depre <- stan_glmer(
  los ~
    Depression.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.depre,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## Diabetes

```{r}
###### bayesian
stan.uni.nb.ri.diab <- stan_glmer(
  los ~
    Diab.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.diab,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## EoE

```{r}
###### bayesian
stan.uni.nb.ri.eoe <- stan_glmer(
  los ~
    EoE.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 1),
  prior_intercept = normal(0, 1),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.eoe,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## FA

```{r}
###### bayesian
stan.uni.nb.ri.fa <- stan_glmer(
  los ~
    FA.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)
coefs<-mcmc_post_ci(stan.uni.nb.ri.fa,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## GERD

```{r}
###### bayesian
stan.uni.nb.ri.gerd <- stan_glmer(
  los ~
    GERD.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.gerd,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## HTA

```{r}
###### bayesian
stan.uni.nb.ri.hta <- stan_glmer(
  los ~
    HTA.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.hta,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## Obesity

```{r}
###### bayesian
stan.uni.nb.ri.obs <- stan_glmer(
  los ~
    OBST.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.obs,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## Sleep apnea

```{r}
###### bayesian
stan.uni.nb.ri.apnea <- stan_glmer(
  los ~
    APNEA.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.apnea,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```


## Psoriasis

```{r}
###### bayesian
stan.uni.nb.ri.psor <- stan_glmer(
  los ~
    PSOR.lon +
    (1 | id)+(1 | ehrsite),
  data = data,
  family = neg_binomial_2,
  prior = normal(0, 2.5),
  prior_intercept = normal(0, 5),
  chains=4,
  cores=8,refresh=50,
  iter=1200,QR=F,
  seed = 12345
)

coefs<-mcmc_post_ci(stan.uni.nb.ri.psor,0.95,34)$df
coefs %>% dplyr::select(HR)

#cp
save.image("data/asthma.los.univariate.full.rstanarm.v7.RData")
```



```{r}

```
