---
title: "Asthma Length of stay"
output:
  html_document: default
  pdf_document: default
date: "2023-06-02"
---

v1

1. Dataset: aou_los_v1.RData
2. EDA for los
3. Univariate for los

v2

1. Dataset: aou_los_v2.RData

v3

1. Dataset: aou_los_v3.RData
2. Additional comorbidities
3. Migrated from splines to splines2 
(Periodic B-splines and Rcpp Armadillo performance boost) https://cran.r-project.org/web/packages/splines2/vignettes/splines2-intro.html#b-spline-basis-functions
4. Several models tested: Zero inflated negative binomial, GAMMs

v4
Dataset: aou_los_v6.RData


v5
pico dataset using stratified sampling by race
Code cleanup
Only NB MCMC
EHR site added

v6
use of asthma.los.multivariate.full.rstanarm.v6.RData


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning = F,results = T)
rm(list = ls())

library(tidyverse)
library(foreign)
library(patchwork)
library(MASS)
library(lubridate)
library(lme4)
library(splines2)
library(rstanarm)
library(bayesplot)
color_scheme_set("mix-teal-pink")
bayesplot_theme_set(theme_minimal())
cbPalette <- c("#E64B35", "#4DBBD5")

load("data/asthma.los.multivariate.full.rstanarm.v6.RData")

# source("helpers.R")
```



```{r}
ppd <- posterior_predict(stan.nb.ri.full, draws=500)
ppd %>%
  ppc_intervals(y = stan.nb.ri.full$glmod$fr$los, yrep = ., fatten = 0, 
              x = stan.nb.ri.full$glmod$fr$ehrsite, prob = .95) +
  labs(x = "EHR site", y = "los",
       title = "95% posterior predictive intervals vs real values")+
  panel_bg(fill="gray90", color = NA) +
 grid_lines(color = "white")

```





```{r}
ppd %>%
  ppc_intervals_grouped(y = stan.nb.ri.full$glmod$fr$los, yrep = .,
                        group = stan.nb.ri.full$glmod$fr$race3, fatten = 0, 
              x = stan.nb.ri.full$glmod$fr$dep_idx, prob = .95) +
  labs(x = "Deprivation (%)", y = "los",
       title = "95% posterior predictive intervals vs real values")+
  panel_bg(fill="gray90", color = NA) +
 grid_lines(color = "white")

```


```{r}
disLabels<-c(
    "exp(ageatvisit:sex_at_birthMale)" = "Age:Male",
    "exp(ageatvisit:sex_at_birthFemale)" = "Age:Female",
    "exp(s.age:sex_at_birthMale)" = "Age:Male",
    "exp(s.age:sex_at_birthFemale)" = "Age:Female",
    
    "exp(race3Asian)" = "Asian",
    "exp(race3Black_AA)" = "Black",
    "exp(race3HL)" = "HL",
    "exp(race3MENA)" = "MENA",
    "exp(race3White_EA)" = "White",
    "exp(race3Asian:dep_idx)" = "Deprivation:Asian",
    "exp(race3Black_AA:dep_idx)" = "Deprivation:Black",
    "exp(race3HL:dep_idx)" = "Deprivation:HL",
    "exp(race3MENA:dep_idx)" = "Deprivation:MENA",
    "exp(race3White_EA:dep_idx)" = "Deprivation:White",
    "exp(dep_idx:race3Asian)" = "Deprivation:Asian",
    "exp(dep_idx:race3Black_AA)" = "Deprivation:Black",
    "exp(dep_idx:race3HL)" = "Deprivation:HL",
    "exp(dep_idx:race3MENA)" = "Deprivation:MENA",
    "exp(dep_idx:race3White_EA)" = "Deprivation:White",
    "exp(dep_idx)" = "Deprivation",
    "exp(s.dep)" = "Deprivation",
    
    "exp(hcType1Public)" = "Insurance:Public",
    
    "exp(seasonFall)" = "Fall",
    "exp(seasonWinter)" = "Winter",
    "exp(seasonSpring)" = "Spring",
    "exp(weekendWeekend)"="Admission:Weekend",
    "exp(AD.lonTRUE)" = "AD",
    "exp(AR.lonTRUE)" = "AR",
    "exp(EoE.lonTRUE)" = "EoE",
    "exp(FA.lonTRUE)"="FA",
    "exp(GERD.lonTRUE)" = "GERD",
    "exp(OBST.lonTRUE)" = "Obesity",
    "exp(PSOR.lonTRUE)" = "Psoriasis",
    "exp(APNEA.lonTRUE)"="Apnea",
    
    "exp(Cancer.lonTRUE)" = "Cancer",
    "exp(CHD.lonTRUE)"="CHD",
    "exp(CKD.lonTRUE)" = "CKD",
    "exp(COPD.lonTRUE)" = "COPD",
    "exp(Depression.lonTRUE)" = "Depression",
    "exp(Diab.lonTRUE)"="Diabetes",
    "exp(HTA.lonTRUE)"="HTA"
    )
```



# full d no interaction

```{r}
pDemo<-mcmc_intervals(stan.nb.ri.full.d,regex_pars = "age|race|hc|season|week|dep",  prob = 0.95,transformations = "exp") +
 labs(
   title = "Posterior distributions with medians and 95% intervals",
   subtitle = "Demographics, temporal & place-based",x="Expected LOS"
 )+geom_vline(xintercept =1,lty="dashed",alpha=0.5)+
  scale_y_discrete(
    limits=rev(c(
    "exp(s.age:sex_at_birthMale)",
    "exp(s.age:sex_at_birthFemale)",
    "exp(race3Asian)",
    "exp(race3Black_AA)",
    "exp(race3HL)",
    "exp(race3MENA)",
    "exp(hcType1Public)",
    "exp(weekendWeekend)"
    ))
    ,
    
    labels=disLabels
    )

pDemo+
   coord_cartesian(xlim=c(0.6, 1.3))
```


```{r}
pDise1<-mcmc_intervals(stan.nb.ri.full.d,regex_pars = "AD|AR|EoE|FA|GERD|OBS|PSOR|APNE",  prob = 0.95,transformations = "exp") +
 labs(
   # title = "Posterior distributions with medians and 95% intervals",
   subtitle = "Previous comorbidities (Non-chronic diseases)",x="Expected LOS"
 )+geom_vline(xintercept =1,lty="dashed",alpha=0.5)+
  scale_y_discrete(
    limits=rev(c(
    # "exp(AD.lonTRUE)",
    "exp(AR.lonTRUE)",
    # "exp(EoE.lonTRUE)",
    # "exp(FA.lonTRUE)",
    "exp(GERD.lonTRUE)",
    "exp(OBST.lonTRUE)",
    # "exp(PSOR.lonTRUE)",
    "exp(APNEA.lonTRUE)"
    ))
    ,
    
    labels=disLabels
    )
# +
#   xlim(0.0,2.5)

pDise1
```


```{r}
pDise2<-mcmc_intervals(stan.nb.ri.full.d,regex_pars = "Cance|CHD|CKD|COPD|Depr|Diab|HTA",  prob = 0.95,transformations = "exp") +
 labs(
   # title = "Posterior distributions with medians and 95% intervals",
   subtitle = "Previous comorbidities (chronic diseases)",x="Expected LOS"
 )+geom_vline(xintercept =1,lty="dashed",alpha=0.5)+
  scale_y_discrete(
    limits=rev(c(
    "exp(Cancer.lonTRUE)",
    "exp(CHD.lonTRUE)",
    "exp(CKD.lonTRUE)",
    "exp(COPD.lonTRUE)",
    "exp(Depression.lonTRUE)",
    "exp(Diab.lonTRUE)",
    "exp(HTA.lonTRUE)"
    ))
    ,
    
    labels=disLabels
    )


pDise2
```


```{r}
ppd <- posterior_predict(stan.nb.ri.ehrsite, draws=1000)
ppd %>%
  ppc_intervals(y = stan.nb.ri.ehrsite$data$los, yrep = ., fatten = 0, 
              x = stan.nb.ri.ehrsite$data$ehrsite, prob = 0.95) +
  labs(x = "EHR site", y = "los",
       title = "50% posterior predictive intervals vs real values")+
  panel_bg(fill="gray90", color = NA) +
 grid_lines(color = "white")

```


```{r}
ppd <- posterior_predict(stan.nb.ri.full, draws=500)
ppd %>%
  ppc_stat_grouped(y = stan.nb.ri.full$glmod$fr$los, yrep = .,
                   group = stan.nb.ri.full$glmod$fr$race3,
                   stat = "median", binwidth=0.005)
```




# Handling overdispersion

```{r}
prop_zero <- function(y) mean(y == 0)
prop_zero_test1 <- pp_check(stan.ps.ri.null, plotfun = "stat", stat = "prop_zero", binwidth = .001)
prop_zero_test2 <- pp_check(stan.nb.ri.null, plotfun = "stat", stat = "prop_zero",binwidth = .001)
prop_zero_test3 <- pp_check(stan.nb.ri.full.d, plotfun = "stat", stat = "prop_zero",binwidth = 0.001)


(prop_zero_test1 + ggtitle("Poisson")+coord_cartesian(xlim=c(0.33, 0.48)))+
  (prop_zero_test3 + ggtitle("NB")+coord_cartesian(xlim=c(0.33, 0.48)))+
  patchwork::plot_layout(guides = "collect")
```








```{r}
yrep_poisson <- posterior_predict(stan.ps.ri.null, draws = 200)
yrep_nb <- posterior_predict(stan.nb.ri.full, draws = 200)
dim(yrep_poisson)
```


```{r}
y <- example_y_data()
yrep <- example_yrep_draws()
ppc_error_hist(y, yrep[1:3, ])
```




```{r}

# Data is the initial data frame
# Model is the final data frame used in Stan, 
# color_scheme_set("brightblue")
a<-ppc_dens_overlay(stan.ps.ri.null$glmod$fr$los, yrep_poisson)+xlim(0,15)+ggtitle("Stan Poisson")
b<-ppc_dens_overlay(stan.nb.ri.full$glmod$fr$los, yrep_nb)+xlim(0,15)+ggtitle("Stan Negative Binomial")

a+b
# pp_check(stan_glm2, type = "overlaid", ndraws = 100)+xlim(0,15)
```

